**The status of the microbial census: an update**

### 2015-11-18 Schloss_Census2_mBio_2015.Rmd
Add some ideas to Results section outline

>>>>

* What does the ongonig census look like?
  - flat
* Why might it be flat?
  - Good's coverage
  - Schloss's coverage
  - % of NGS reads that map to database
* Why aren't we doig a great job?
  - Rate of change in full-length sequences has plateaued
  - New sequences are submitted by a small number of investigators for a limited number of environments
* What can we do to fix this?
  - Characterize coverage by environments
  - Cultured vs. uncultured
  - Single cell genomics
